Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-11-19 paper/ifo-appendix.tex
full grammar check before submission

\section{Detecting a sinusoidal signal in Gaussian noise}
\label{app:sinusoid_likelihood}
%\jam{[to do! from Andrew: ``Write a short appendix proving that maximizing the likelihood exp(-n||n/2) with respect to A given a signal A cos (wt + phi) is the Fourier transform. Classic sig proc result useful for teachers to know.'']}
In this appendix, we demonstrate the the modulus of the Fourier Transform is an appropriate detection statistic when searching for a sinusoidal signal in Gaussian noise. 
We describe the data as
\begin{equation}
x(t) = s(t) + n(t)\,, 
\end{equation}
where $s(t)$ and $n(t)$ are the signal and noise respectively. 
Then we describe the signal as 
\begin{equation}
s(t) = A \cos{\omega t + \phi}\,,
\end{equation}
where $A$, $\omega$, and $\phi$ are the amplitude, angular frequency and phase of the signal respectively. 
The log likelihood assuming Gaussian noise is given by
\begin{eqnarray}
\log \mathcal{L} &=& -\frac{1}{2}\ip{n}{n}\,, \\
                 &=& -\frac{1}{2}\ip{x-s}{x-s}\,, \\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{2} \ip{\cos[\omega t + \phi]}{\cos[\omega t + \phi]} \nonumber\\
                 &&+ A \ip{x}{\cos[\omega t + \phi]}\,,\\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{4} + A \ip{x}{\cos[\omega t + \phi]}\,,\label{eqn:logLike}
\end{eqnarray}
where we define the inner product between $u(t)$ and $v(t)$ as $\ip{u}{v} = \int_0^T \mathrm{d} t \, u(t) v(t) $ and $T$ is the total time of the data (and the last line assumes that $T\gg1/\omega$ so that $\ip{\cos[\omega t + \phi]}{\cos[\omega t + \phi]}\approx{1/2}$).

>>>>

\section{Detecting a sinusoidal signal in Gaussian noise}
\label{app:sinusoid_likelihood}
%\jam{[to do! from Andrew: ``Write a short appendix proving that maximizing the likelihood exp(-n||n/2) with respect to A given a signal A cos (wt + phi) is the Fourier transform. Classic sig proc result useful for teachers to know.'']}
In this appendix, we demonstrate the modulus of the Fourier transform is an appropriate detection statistic when searching for a sinusoidal signal in Gaussian noise. 
We describe the data as
\begin{equation}
x(t) = s(t) + n(t)\,, 
\end{equation}
where $s(t)$ and $n(t)$ are the signal and noise respectively. 
Then we describe the signal as 
\begin{equation}
s(t) = A \cos{\omega t + \phi}\,,
\end{equation}
where $A$, $\omega$, and $\phi$ are the amplitude, angular frequency and phase of the signal respectively. 
The log likelihood assuming Gaussian noise is given by
\begin{eqnarray}
\log \mathcal{L} &=& -\frac{1}{2}\ip{n}{n}\,, \\
                 &=& -\frac{1}{2}\ip{x-s}{x-s}\,, \\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{2} \ip{\cos[\omega t + \phi]}{\cos[\omega t + \phi]} \nonumber\\
                 &&+ A \ip{x}{\cos[\omega t + \phi]}\,,\\ 
                 &=& -\frac{1}{2}\ip{x}{x} - \frac{A^2}{4} + A \ip{x}{\cos[\omega t + \phi]}\,,\label{eqn:logLike}
\end{eqnarray}
where we define the inner product between $u(t)$ and $v(t)$ as $\ip{u}{v} = \int_0^T \mathrm{d} t \, u(t) v(t) $ and $T$ is the total time of the data (and the last line assumes that $T\gg1/\omega$ so that $\ip{\cos[\omega t + \phi]}{\cos[\omega t + \phi]}\approx{1/2}$).

### 2020-11-19 paper/ifo-complexAudio.tex
full grammar check before submission

% Optical microphone
% aim of optical microphone: play back injected sounds
% some editing in response to pnp
In this section, we explore how this demonstration can be used to teach a selection of signal processing techniques.
The apparatus used in Sections~\ref{sec:ifo} to~\ref{sec:viterbi_wandering} affords the opportunity to explore a range of signal processing techniques and filters of interest to undergraduate students and provide a foundations for many technical applications~\cite{DigitalProcingOfSpeechSignals:1978}. 
We provide a series of example activities using complex audio (such as music and speech) as a natural successor to constant and wandering tones. 
%A natural successor to constant and wandering tones is complex audio, such as music and speech. 
As complex audio signals are not quasi-monochromatic, unlike continuous gravitational wave signals, the Viterbi algorithm as implemented in Section~\ref{sec:viterbi_wandering} is not directly applicable here. Instead, in this section, we use the interferometer as an ``optical microphone'' to detect and play back complex audio signals (i.e.\ using light to capture sound).
In doing so, we experiment with a hierarchy of passive filters which suppress noise, yet make no assumption about the specific form of the signal, unlike the Fourier-based maximum likelihood matched filter which is tuned to the sinusoidal signals in Section~\ref{sec:single_tone} and Appendix~\ref{app:sinusoid_likelihood}.
A vast literature exists on signal processing with speech, see Ref.~\cite{DigitalProcingOfSpeechSignals:1978} for introductory material including Fourier analysis and digital representations.
Optical microphone devices have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defence industry and operate on a variety of related principles.

@@

We place a OSRAM BPW21 photodiode in reverse-bias over an LM358 op-amp which together make a photo-detector that produces a voltage dependent on the incident intensity. 
The photodiode records the interference pattern at roughly the same off-centre position as the webcam in Sections~\ref{sec:single_tone} and~\ref{sec:viterbi_wandering}, again chosen arbitrarily.
The photodiode is mounted on a cloth screen re-purposed from the dismantled commercial speaker, with the electrical leads connected underneath the screen. 
The voltage signal from the photo-detector is captured by a MCP3008 $10$-bit analog-to-digital converter (ADC) connected to a Raspberry Pi Model 3 v1.2~\cite{RaspberryPi:online} (henceforth: Pi), which provides a convenient means to record the photodiode data.
Together, the circuit samples the signal at $\sim 16\,{\rm kHz}$. Resources for using the Pi and photodiode are described in Appendix~\ref{app:circuit_diagram}.

@@

Results for a selection of filters are collated in Fig.~\ref{fig:BackgroundNotchWienerCombined} where the left and right columns show timeseries and Fourier spectrum results, respectively. 
The first and second rows of Fig.~\ref{fig:BackgroundNotchWienerCombined} show the source signal and the raw optical microphone recording, respectively. 
The third row shows a background spectrum of the optical microphone, as shown previously in the top panel Fig.~\ref{fig:psd_noise}.

@@

Although the notch filter removes much of the mains hum sound, the filtered recording is not intelligible. Qualitatively it sounds more like a drum than a human voice. Evidently, this is due to loss of voice information under the filter.

@@

% \begin{figure*}
% \begin{center}
% \includegraphics[width=\textwidth,trim={1cm 8.2cm 1 8.3cm},clip]{figures/timeSeriesNotchWiener.pdf}
% \end{center}
% \caption{\label{fig:timeNotchWiener}
% Timeseries results for the notch and Wiener filters. 
% The first panel shows the original speech recording which was played from the speaker. 
% The second panel shows the data from the optical microphone before any filters are applied. 
% The third and fourth panels show results after applying the notch and Wiener filter respectively. 
% Finally, the fifth panel shows the result of applying both the notch and Wiener filter. 
% }
% \end{figure*}

% \begin{figure*}
% \begin{center}
% \includegraphics[width=\textwidth,trim={0cm 8.2cm 0cm 8cm},clip]{figures/freqNotchWiener.pdf}
% \end{center}
% \caption{\label{fig:freqNotchWiener}
% Frequency spectrum results for the notch and Wiener filters. 
% The first and second panels show the results of applying the notch and Wiener filter respectively.
% The third panel shows the spectrum after applying both the notch and Wiener filters. 
% The first, second, and third panels show the spectrum of the timeseries show in the third, fourth, and fifth panels of Fig.~\ref{fig:timeNotchWiener} respectively. 
% }
% \end{figure*}

@@

%As an instructive aside, i
If we let the Wiener filter be non-causal (i.e. we estimate the current signal based on both past \emph{and future} observations), then we can represent Eqn.~\ref{eqn:wiener-hopf} in the frequency domain as
\begin{equation}
\label{eqn:wiener}
    H(f)=\frac{P_{ss}(f)}{P_{xx}(f)}=\frac{P_{ss}(f)}{P_{ss}(f)+P_{ww}(f)}
\end{equation}
where $P_{xx}(f), P_{ss}(f), P_{ww}(f)$ are the spectra of the observed noisy data, the injected signal, and the background noise, respectively. Intuitively, from Eqn.~\ref{eqn:wiener}, we can see that the non-causal Wiener filter amplifies the input signal where the signal to noise ratio (SNR) is high, and attenuates the signal where the SNR is low. The causal Wiener filter (that only makes estimates based on past observations) is similar. More detailed analysis of both kinds of Wiener filters can be found in Ref.~\citep{10.5555/151045}.
% That this filter is non-causal makes it unsuitable for real time signal processing

@@

In this work, we construct a higher-order causal Wiener filter based on Eqn.~\ref{eqn:wiener-hopf}. A higher-order Wiener filter provides greater smoothing of the input signal but also increases the computational memory required. For this work, we choose a Wiener filter of order $n=100$ as it provides a reasonable balance between smoothing and efficiency. The time series and frequency spectrum after applying the Wiener filter are shown in the sixth row of Fig.~\ref{fig:BackgroundNotchWienerCombined}.
We see a significant improvement in the time series of the recovered signal, however a strong noise hum persists, audibly. 
%The Wiener filter produces an estimated signal $\hat{x}$ using linear time-invariant filtering. 
%It minimizes the mean square error $\mathbb{E}[(\hat{x}-x)^2]$ between $\hat{x}$ and the actual signal $x$~\citep{verhoeven2009robust}.
%\han{should we add more details here too?} \jam{[seconded]}
%The timeseries and frequency spectrum results of the Wiener filter are shown in the fourth panel of Fig.~\ref{fig:timeNotchWiener} and the second panel of Fig.~\ref{fig:freqNotchWiener} respectively. 
%The timeseries is visibly cleaner, however there is a strong noise hum.

@@

The Wiener filter makes use of statistical information from the speech data and noise. It amplifies the part of the signal with high SNR, while suppressing the parts with low SNR (see above Sec.~\ref{sec:Wiener}). It is implemented in the form of a finite response filter, which ensures linear phase response and stability (both desirable), but at the cost of high orders computationally. By comparison, the notch filter is based on directly removing the unwanted frequency components. It is implemented in the form of an infinite impulse response filter. Although it significantly decreases the order of the overall filter, it unavoidably introduces nonlinear phase and instability.

By combining the notch and Wiener filter, we can trade off between the two and achieve an overall better performance, as can be seen in the bottom row of Fig.~\ref{fig:BackgroundNotchWienerCombined}..
The filtered voice after the combined notch and Wiener filter is enhanced compared to either alone. The mains noise is all but removed and more voice information is retained. However, the recovered voice still sounds muffled and is not understandable.

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_timeseries_melatos_shift_source.pdf}
	\caption{Time series of an adult male voice (saying ``A cathode ...'') showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). The source signal is shifted by $0.12$ s to the right to synchronise the manual delay from starting to play the source through the speaker and starting the recording at the Raspberry Pi. One second of the one minute recording is shown. The rise at the start of the bottom panel is expected when filtering a signal of finite duration.}
	\label{fig:logMMSE_timeseries}
\end{figure*}

@@

The results of the logMMSE estimator are shown in Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum}. The top two panels of each figure show the original speech signal and anti-aliased reading from the optical microphone for ease of comparison. The third panel of Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum} shows the time series and corresponding spectral amplitude respectively after applying the logMMSE estimator. We see significant attenuation of the mains harmonics as well as a general smoothing of the spectrum. The logMMSE method indeed removes most of the background noise, but does not significantly enhance the speech as the voice sounds muffled and indistinct.
% suggest remove as it's just rephrasing what's already been said
%, with the words unable to be understood.

>>>>

% Optical microphone
% aim of optical microphone: play back injected sounds
% some editing in response to pnp
In this section, we explore how this demonstration can be used to teach a selection of signal processing techniques.
% changed ``affords the opportunity to explore'' to ``allows exploring''
The apparatus used in Sections~\ref{sec:ifo} to~\ref{sec:viterbi_wandering} allows undergraduate students to explore a range of signal processing techniques and filters of interest and provides a foundation for many technical applications~\cite{DigitalProcingOfSpeechSignals:1978}. 
We provide a series of example activities using complex audio (such as music and speech) as a natural successor to constant and wandering tones. 
%A natural successor to constant and wandering tones is complex audio, such as music and speech. 
As complex audio signals are not quasi-monochromatic, unlike continuous gravitational wave signals, the Viterbi algorithm as implemented in Section~\ref{sec:viterbi_wandering} is not directly applicable here. Instead, in this section, we use the interferometer as an ``optical microphone'' to detect and playback complex audio signals (i.e.\ using light to capture sound).
In doing so, we experiment with a hierarchy of passive filters which suppress noise, yet make no assumption about the specific form of the signal, unlike the Fourier-based maximum likelihood matched filter which is tuned to the sinusoidal signals in Section~\ref{sec:single_tone} and Appendix~\ref{app:sinusoid_likelihood}.
A vast literature exists on signal processing with speech, see Ref.~\cite{DigitalProcingOfSpeechSignals:1978} for introductory material including Fourier analysis and digital representations.
Optical microphone devices have precedence in the laser microphones~\cite{laser_microphone} which are (or were historically) used in the defence industry and operate on a variety of related principles.

@@

We place an OSRAM BPW21 photodiode in reverse-bias over an LM358 op-amp which together make a photo-detector that produces a voltage dependent on the incident intensity. 
The photodiode records the interference pattern at roughly the same off-centre position as the webcam in Sections~\ref{sec:single_tone} and~\ref{sec:viterbi_wandering}, again chosen arbitrarily.
The photodiode is mounted on a cloth screen re-purposed from the dismantled commercial speaker, with the electrical leads connected underneath the screen. 
The voltage signal from the photo-detector is captured by an MCP3008 $10$-bit analog-to-digital converter (ADC) connected to a Raspberry Pi Model 3 v1.2~\cite{RaspberryPi:online} (henceforth: Pi), which provides a convenient means to record the photodiode data.
Together, the circuit samples the signal at $\sim 16\,{\rm kHz}$. Resources for using the Pi and photodiode are described in Appendix~\ref{app:circuit_diagram}.

@@

Results for a selection of filters are collated in Fig.~\ref{fig:BackgroundNotchWienerCombined} where the left and right columns show time series and Fourier spectrum results, respectively. 
The first and second rows of Fig.~\ref{fig:BackgroundNotchWienerCombined} show the source signal and the raw optical microphone recording, respectively. 
The third row shows a background spectrum of the optical microphone, as shown previously in the top panel Fig.~\ref{fig:psd_noise}.

@@

Although the notch filter removes much of the mains hum sound, the filtered recording is not intelligible. Qualitatively it sounds more like a drum than a human voice. This is due to loss of voice information under the filter.

@@

% \begin{figure*}
% \begin{center}
% \includegraphics[width=\textwidth,trim={1cm 8.2cm 1 8.3cm},clip]{figures/time SeriesNotchWiener.pdf}
% \end{center}
% \caption{\label{fig:timeNotchWiener}
% Time series results for the notch and Wiener filters. 
% The first panel shows the original speech recording which was played from the speaker. 
% The second panel shows the data from the optical microphone before any filters are applied. 
% The third and fourth panels show results after applying the notch and Wiener filter respectively. 
% Finally, the fifth panel shows the result of applying both the notch and Wiener filter. 
% }
% \end{figure*}

% \begin{figure*}
% \begin{center}
% \includegraphics[width=\textwidth,trim={0cm 8.2cm 0cm 8cm},clip]{figures/freqNotchWiener.pdf}
% \end{center}
% \caption{\label{fig:freqNotchWiener}
% Frequency spectrum results for the notch and Wiener filters. 
% The first and second panels show the results of applying the notch and Wiener filter respectively.
% The third panel shows the spectrum after applying both the notch and Wiener filters. 
% The first, second, and third panels show the spectrum of the time series show in the third, fourth, and fifth panels of Fig.~\ref{fig:timeNotchWiener} respectively. 
% }
% \end{figure*}

@@

%As an instructive aside, i
If we let the Wiener filter be non-causal (i.e. we estimate the current signal based on both past \emph{and future} observations), then we can represent Eqn.~\ref{eqn:wiener-hopf} in the frequency domain as
\begin{equation}
\label{eqn:wiener}
    H(f)=\frac{P_{ss}(f)}{P_{xx}(f)}=\frac{P_{ss}(f)}{P_{ss}(f)+P_{ww}(f)}
\end{equation}
where $P_{xx}(f), P_{ss}(f), P_{ww}(f)$ are the spectra of the observed noisy data, the injected signal, and the background noise, respectively. Intuitively, from Eqn.~\ref{eqn:wiener}, we can see that the non-causal Wiener filter amplifies the input signal where the signal to noise ratio (SNR) is high and attenuates the signal where the SNR is low. The causal Wiener filter (that only makes estimates based on past observations) is similar. More detailed analysis of both kinds of Wiener filters can be found in Ref.~\citep{10.5555/151045}.
% That this filter is non-causal makes it unsuitable for real time signal processing

@@

In this work, we construct a higher-order causal Wiener filter based on Eqn.~\ref{eqn:wiener-hopf}. A higher-order Wiener filter provides greater smoothing of the input signal but also increases the computational memory required. For this work, we choose a Wiener filter of order $n=100$ as it provides a reasonable balance between smoothing and efficiency. The time series and frequency spectrum after applying the Wiener filter are shown in the sixth row of Fig.~\ref{fig:BackgroundNotchWienerCombined}.
We see a significant improvement in the time series of the recovered signal, however, a strong noise hum persists, audibly. 
%The Wiener filter produces an estimated signal $\hat{x}$ using linear time-invariant filtering. 
%It minimizes the mean square error $\mathbb{E}[(\hat{x}-x)^2]$ between $\hat{x}$ and the actual signal $x$~\citep{verhoeven2009robust}.
%\han{should we add more details here too?} \jam{[seconded]}
%The time series and frequency spectrum results of the Wiener filter are shown in the fourth panel of Fig.~\ref{fig:timeNotchWiener} and the second panel of Fig.~\ref{fig:freqNotchWiener} respectively. 
%The time series is visibly cleaner, however there is a strong noise hum.

@@

The Wiener filter makes use of statistical information from the speech data and noise. It amplifies the part of the signal with high SNR while suppressing the parts with low SNR (see above Sec.~\ref{sec:Wiener}). It is implemented in the form of a finite response filter, which ensures linear phase response and stability (both desirable), but at the cost of high orders computationally. By comparison, the notch filter is based on directly removing the unwanted frequency components. It is implemented in the form of an infinite impulse response filter. Although it significantly decreases the order of the overall filter, it unavoidably introduces nonlinear phase and instability.

By combining the notch and Wiener filter, we can trade-off between the two and achieve an overall better performance, as can be seen in the bottom row of Fig.~\ref{fig:BackgroundNotchWienerCombined}.
The filtered voice after the combined notch and Wiener filter is enhanced compared to either alone. The mains noise is all but removed and more voice information is retained. However, the recovered voice still sounds muffled and is not understandable.

@@

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{figures/combined_timeseries_melatos_shift_source.pdf}
	\caption{Time series of an adult male voice (saying ``A cathode ...'') showing the source (top panel), the optical microphone recording (middle panel), and the recording after filtering with the logMMSE estimator (bottom panel). The source signal is shifted by $0.12$ s to the right to synchronise the manual delay from starting to play the source through the speaker and starting the recording at the Raspberry Pi. One second of the one minute long recording is shown. The rise at the start of the bottom panel is expected when filtering a signal of finite duration.}
	\label{fig:logMMSE_timeseries}
\end{figure*}

@@

The results of the logMMSE estimator are shown in Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum}. The top two panels of each figure show the original speech signal and anti-aliased reading from the optical microphone for ease of comparison. The third panel of Figs.~\ref{fig:logMMSE_timeseries} and~\ref{fig:logMMSE_spectrum} shows the time series and corresponding spectral amplitude respectively after applying the logMMSE estimator. We see significant attenuation of the mains harmonics as well as a general smoothing of the spectrum. The logMMSE method indeed removes most of the background noise but does not significantly enhance the speech as the voice sounds muffled and indistinct.
% suggest remove as it's just rephrasing what's already been said
%, with the words unable to be understood.

### 2020-11-19 paper/ifo-conclusions.tex
full grammar check before submission

In this paper, we use a table-top Michelson interferometer as an analogue to a gravitational wave detector, demonstrating a range of signal processing techniques used within the gravitational wave community and more broadly. 
Gravitational wave signals are simulated by playing sound recordings through a speaker fixed to the back of one of the arm mirrors. 
We consider quasi-monochromatic signals as an analogue to continuous wave signals to directly demonstrate techniques used in current continuous gravitational wave searches.
We then consider more complex audio (music and speech) for a more general interest in signal processing and explore use of the interferometer as an optical microphone. 
A variety of example activities are presented. 
We find that the logMMSE produces the best results, however it does not enhance the recording to an intelligible level. 
The complex audio signals can also serve as more distant analogues to un-modelled gravitaitonal-wave burst signals, e.g. from supernova.

@@

The demonstration presented has potential to be adapted for use in the undergraduate laboratory.
It can be used to teach topics of interest to physics and electrical engineering students including, interferometer physics; gravitational wave detection, searches, and analysis; and signal processing with filters and speech enhancement techniques. 
The increased excitement and public interest in the field of gravitational wave research in recent years means that this demonstration may also be adapted as a tool for explaining gravitational wave research to a wider, non-specialist audience. 
The field of gravitational wave astrophysics continuous to grow and the future will bring many more detections of binary black holes and neutron stars, as well as the anticipated first detection of other classes of signals, such as continuous waves, to which this demonstration provides some charming insights. 
% \jam{``charming'' is very sweet}
%The demonstration presented here has great potential to be adapted for use in the undergraduate laboratory. It can be used to demonstrate topics such as interferometer physics; gravitational wave detection, searches, and analysis; and signal processing with filters and speech enhancement techniques to physics and electrical engineering students. Given the increased level of excitement and public interest in the field of gravitational wave astronomy in recent years, this table-top demonstration can be used as a tool for explaining gravitational wave research to a wider, non-specialist audience. The future will bring many more detections, including further observations of transient signals from binary black hole and binary neutron star mergers, as well as the anticipated first detections of other classes of signal, including continuous waves, to which this demonstration provides some charming insights.

>>>>

In this paper, we use a table-top Michelson interferometer as an analogue to a gravitational wave detector, demonstrating a range of signal processing techniques used within the gravitational wave community and more broadly. 
Gravitational wave signals are simulated by playing sound recordings through a speaker fixed to the back of one of the arm mirrors. 
We consider quasi-monochromatic signals as an analogue to continuous wave signals to directly demonstrate techniques used in current continuous gravitational wave searches.
We then consider more complex audio (music and speech) for a more general interest in signal processing and explore the use of the interferometer as an optical microphone. 
A variety of example activities is presented. 
We find that the logMMSE produces the best results, however, it does not enhance the recording to an intelligible level. 
The complex audio signals can also serve as more distant analogues to un-modelled gravitational wave burst signals, e.g. from supernovae.

@@

The demonstration presented has the potential to be adapted for use in the undergraduate laboratory.
It can be used to teach topics of interest to physics and electrical engineering students including, interferometer physics; gravitational wave detection, searches, and analysis; and signal processing with filters and speech enhancement techniques. 
The increased excitement and public interest in the field of gravitational wave research in recent years means that this demonstration may also be adapted as a tool for explaining gravitational wave research to a wider, non-specialist audience. 
The field of gravitational wave astrophysics continuous to grow and the future will bring many more detections of binary black holes and neutron stars, as well as the anticipated first detection of other classes of signals, such as continuous waves, to which this demonstration provides some charming insights. 
% \jam{``charming'' is very sweet}
%The demonstration presented here has great potential to be adapted for use in the undergraduate laboratory. It can be used to demonstrate topics such as interferometer physics; gravitational wave detection, searches, and analysis; and signal processing with filters and speech enhancement techniques to physics and electrical engineering students. Given the increased level of excitement and public interest in the field of gravitational wave astronomy in recent years, this table-top demonstration can be used as a tool for explaining gravitational wave research to a wider, non-specialist audience. The future will bring many more detections, including further observations of transient signals from binary black hole and binary neutron star mergers, as well as the anticipated first detections of other classes of signal, including continuous waves, to which this demonstration provides some charming insights.

### 2020-11-19 paper/ifo-futureWork.tex
full grammar check before submission

% reduced length
Isolating the experiment from interference may provide some reduction in noise. 
For example, the Raspberry Pi could be powered with a commercial battery instead of mains power. 
%An initial improvement could be to better isolate the experiment, especially from the sources of mains noise. 
%As the Raspberry Pi demands little power and connects to USB it could instead be powered with a commercial battery rather than the mains supply. 
All other components of the circuit draw power from the Pi, so this would isolate the circuit from the mains. 
%All other components of the circuit, including the photodiode are connected to the Pi. 
The laser is DC powered through a converter, so should not couple noise from the mains into the interferometer. 
Transferring the circuit from a breadboard to a printed circuit board can also reduce interference~\cite{elfekey2013design}.
%With the interferometer in a dark room and under a box to better isolate from any ambient light or air currents, this would hopefully remove (or better separate) all sources of the 50Hz mains hum from the optical microphone.
A feedback loop control system can also be used to suppress unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}, similar to methods used to isolate gravitational wave observatories. 
%We can consider improving the stability of the optical microphone components. A feedback loop control system can be used to suppress any unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}.

@@

A voluminous literature exists on using hidden Markov models trained on phonemes to recognize speech~\cite{HMM_english}. These could perform the final stage of speech enhancement for the optical microphone. Interestingly, this coincidently connects back to the Viterbi algorithm in Section~\ref{sec:viterbi_wandering}, which is also underpinned by a hidden Markov model, albeit of a different type. Alternatively, machine learning solutions exist throughout the field that are able to compete with statistical techniques such as the logMMSE estimator~\cite{SEGAN}.

>>>>

% reduced length
Isolating the experiment from interference may provide some noise reduction. 
For example, the Raspberry Pi could be powered with a commercial battery instead of mains power. 
%An initial improvement could be to better isolate the experiment, especially from the sources of mains noise. 
%As the Raspberry Pi demands little power and connects to USB it could instead be powered with a commercial battery rather than the mains supply. 
All other components of the circuit draw power from the Pi, so this would isolate the circuit from the mains. 
%All other components of the circuit, including the photodiode are connected to the Pi. 
The laser is DC powered through a converter, so should not couple noise from the mains into the interferometer. 
Transferring the circuit from a breadboard to a printed circuit board can also reduce interference~\cite{elfekey2013design}.
%With the interferometer in a dark room and under a box to better isolate from any ambient light or air currents, this would hopefully remove (or better separate) all sources of the 50Hz mains hum from the optical microphone.
A feedback loop control system can also be used to suppress any unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}, similar to methods used to isolate gravitational wave observatories. 
%We can consider improving the stability of the optical microphone components. A feedback loop control system can be used to suppress any unwanted movement of the interferometer components~\citep{abbott2017exploring, Sekiguchi:2016bmv, verhoeven2009robust}.

@@

A voluminous literature exists on using hidden Markov models trained on phonemes to recognize speech~\cite{HMM_english}. These could perform the final stage of speech enhancement for the optical microphone. Interestingly, this coincidently connects back to the Viterbi algorithm in Section~\ref{sec:viterbi_wandering}, which is also underpinned by a hidden Markov model, albeit of a different type. Alternatively, machine learning solutions exist throughout the field that can compete with statistical techniques such as the logMMSE estimator~\cite{SEGAN}.
